Title

### 2024-08-30 paper.tex
make intro less wordy

\section{Introduction}
Let \(\mathfrak{g} = \gl_m \times \gl_{m + n}\), with \(n > 0\).
% The nilpotent cone in \(\mathfrak{g}\) is \(\mathcal{N} = \mathcal{N}_m \times \mathcal{N}_{m + n}\), where \(\mathcal{N}_m\) and \(\mathcal{N}_{m + n}\) are the nilpotent cones in \(\gl_m\) and \(\gl_{m + n}\) respectively.
% Let \(\mathcal{B}_m\) and \(\mathcal{B}_{m + n}\) be the varieties of Borel subalgebras of \(\gl_m\) and \(\gl_n\) respectively.
% The variety of Borel subalgebras of \(\mathcal{N}\) is \(\mathcal{B} = \mathcal{B}_m \times \mathcal{B}_{m + n}\).
% Let
% \[\widetilde{\mathcal{N}} := \{(\mathfrak{b}, n) \in \mathcal{B} \times \mathcal{N} : n \in \mathfrak{b}\} = \]
% \[\{(\mathfrak{b}_m, \mathfrak{b}_{m + n}, n_m, n_{m + n}) \in \mathcal{B}_m \times \mathcal{B}_{m + n} \times \mathcal{N}_m \times \mathcal{N}_{m + n} : n_m \in \mathfrak{b}_m, n_{m + n} \in \mathfrak{b}_{m + n}\}.\]
Let \(\pi : \widetilde{\mathcal{N}} \to \mathcal{N} \hookrightarrow \mathfrak{g}\) be the Springer resolution.
\par Let \((e, h, f)\) be the principal \(\spl_2\)-triple in \(\gl_n\).
We have an embedding \(\gl_n \hookrightarrow \gl_m \times \gl_n \hookrightarrow \gl_{m + n}\).
Let \((E, H, F)\) be the \(\spl_2\)-triple in \(\gl_{m + n}\) which is the image of \((e, h, f)\) via this embedding.
Let \(S\) be the Slodowy slice \(E + \mathfrak{z}_{\gl_m}(F)\).
We have a map \(\gl_{m + n} \to \gl_m\) given by coordinate projection.
Restricting to \(S\), we obtain \(f_1 : S \to \gl_m\).
(It turns out that this map is surjective.)
Then, we obtain \(p_1 : S \to \mathfrak{g}\) by \(x \mapsto (x, f_1(x))\).
Taking the map \(p_1 : S \to \mathfrak{g}\) and the Springer resolution \(\widetilde{\mathcal{N}} \to \mathfrak{g}\), we obtain a fibred product \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
\par In this paper we study \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
% The first few sections will be finding what it looks like (in particular, what are the elements of \(S\) which project to nilpotent elements of \(\mathfrak{g}\)), and then we will find the irreducible components of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
As a step towards studying \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\), we consider the map \(S \times_\mathfrak{g} \widetilde{\mathcal{N}} \to \gl_m\) given by taking the map to \(\mathfrak{g}\) and then projecting to \(\gl_m\).
The main section of this paper will study the fibers of this map.
Given \(X \in \mathcal{N}_m \subseteq \gl_m\), we call the fiber at \(X\) the \emph{\(n\)-Slodowy-slice Springer fiber at \(X\)}.
\par In section 2, we review some preliminary material.
In section 3, we find the unique (up to similarity) principal \(\spl_2\)-triple in \(\gl_n\).
In section 4, we embed this \(\spl_2\)-triple into \(\gl_{m + n}\) as described above.
We compute the Slodowy slice, and we end up with a nice description of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
\par In section 5, we discuss how to reduce the problem of finding the irreducible components of an \(n\)-Slodowy-slice Springer fiber at \(X \in \mathcal{N}_m\) to an easier problem.
In section 6 we solve the easier problem.
In section 7 we find the irreducible components of an \(n\)-Slodowy-slice Springer fiber.
In section 8 we apply the results of section 7 to find the irreducible components of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
In section 9 we discuss an interesting direction for future work.
Then in section 10 we prove some linear algebra facts that were used in the paper.

>>>>

\section{Introduction}
Let \(\mathfrak{g} = \gl_m \times \gl_{m + n}\), with \(n > 0\).
% The nilpotent cone in \(\mathfrak{g}\) is \(\mathcal{N} = \mathcal{N}_m \times \mathcal{N}_{m + n}\), where \(\mathcal{N}_m\) and \(\mathcal{N}_{m + n}\) are the nilpotent cones in \(\gl_m\) and \(\gl_{m + n}\) respectively.
% Let \(\mathcal{B}_m\) and \(\mathcal{B}_{m + n}\) be the varieties of Borel subalgebras of \(\gl_m\) and \(\gl_n\) respectively.
% The variety of Borel subalgebras of \(\mathcal{N}\) is \(\mathcal{B} = \mathcal{B}_m \times \mathcal{B}_{m + n}\).
% Let
% \[\widetilde{\mathcal{N}} := \{(\mathfrak{b}, n) \in \mathcal{B} \times \mathcal{N} : n \in \mathfrak{b}\} = \]
% \[\{(\mathfrak{b}_m, \mathfrak{b}_{m + n}, n_m, n_{m + n}) \in \mathcal{B}_m \times \mathcal{B}_{m + n} \times \mathcal{N}_m \times \mathcal{N}_{m + n} : n_m \in \mathfrak{b}_m, n_{m + n} \in \mathfrak{b}_{m + n}\}.\]
Let \(\pi : \widetilde{\mathcal{N}} \to \mathcal{N} \hookrightarrow \mathfrak{g}\) be the Springer resolution.
\par Let \((e, h, f)\) be the principal \(\spl_2\)-triple in \(\gl_n\).
We have an embedding \(\gl_n \hookrightarrow \gl_m \times \gl_n \hookrightarrow \gl_{m + n}\).
Let \((E, H, F)\) be the \(\spl_2\)-triple in \(\gl_{m + n}\) which is the image of \((e, h, f)\) via this embedding.
Let \(S\) be the Slodowy slice \(E + \mathfrak{z}_{\gl_m}(F)\).
We have a map \(\gl_{m + n} \to \gl_m\) given by coordinate projection.
Restricting to \(S\), we obtain \(f_1 : S \to \gl_m\).
(It turns out that this map is surjective.)
Then, we obtain \(p_1 : S \to \mathfrak{g}\) by \(x \mapsto (x, f_1(x))\).
Taking the map \(p_1 : S \to \mathfrak{g}\) and the Springer resolution \(\widetilde{\mathcal{N}} \to \mathfrak{g}\), we obtain a fibred product \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
\par In this paper we study \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
% The first few sections will be finding what it looks like (in particular, what are the elements of \(S\) which project to nilpotent elements of \(\mathfrak{g}\)), and then we will find the irreducible components of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
As a step towards studying \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\), we consider the map \(S \times_\mathfrak{g} \widetilde{\mathcal{N}} \to \gl_m\) given by taking the map to \(\mathfrak{g}\) and then projecting to \(\gl_m\).
The main section of this paper will study the fibers of this map.
Given \(X \in \mathcal{N}_m \subseteq \gl_m\), we call the fiber at \(X\) the \emph{\(n\)-Slodowy-slice Springer fiber at \(X\)}.
\par Section 2 reviews some preliminary material.
Section 3 finds the unique (up to similarity) principal \(\spl_2\)-triple in \(\gl_n\).
Section 4 embeds this \(\spl_2\)-triple into \(\gl_{m + n}\) as described above.
We compute the Slodowy slice and end up with a nice description of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
\par Section 5 discusses how to reduce the problem of finding the irreducible components of an \(n\)-Slodowy-slice Springer fiber at \(X \in \mathcal{N}_m\) to an easier problem.
Section 6 solves the easier problem.
Section 7 finds the irreducible components of an \(n\)-Slodowy-slice Springer fiber.
Section 8 applies the results of section 7 to find the irreducible components of \(S \times_\mathfrak{g} \widetilde{\mathcal{N}}\).
Section 9 discusses an interesting direction for future work.
Finally, section 10 proves some linear algebra lemmas that were used in the paper.
